---
output: github_document
---


```{r, 'setup', echo=FALSE, results="hide", warning=FALSE, message=FALSE}
# Load some libraries
library("knitr")
library("RefManageR")
library("tidyverse")
library("here")
library("patchwork")
library("scholar")
library("textutils")

# Plotting options
opts_chunk$set(fig.width=8, fig.height=5)

my_theme <- function() {
  theme_minimal() + 
    theme(
      plot.title = element_text(size = rel(1), face = "bold"), 
      plot.subtitle = element_text(size = rel(0.9)),
      plot.caption = element_text(color = "#777777", vjust = 0),
      axis.title = element_text(size = rel(.9), hjust = 0.95, face = "italic"), 
      panel.grid.major = element_line(size = rel(.1), color = "grey70"), 
      panel.grid.minor = element_line(size = rel(.1), color = "grey70")
    )
}

```

# mybib

**Last Updated**: `r sprintf("%s", Sys.time())`  
**License**: Public Domain (CC-0)

Version controlled .bib files for my scholarly work, as well as some light 
analyses and a complete reference list.

This repo now includes two main bib files: 
__publications_html.bib__ and __publications_latex.bib__. 

I call these files in to other projects (e.g., cv, personal website) when I 
want to print a list of references. 

Initial commit is a direct copy of example done by 
[leeper](https://github.com/leeper/references). 

----





Load bibs and generate some useful files and dataframes: 

```{r, 'data', message=FALSE, warning=FALSE}
# Load bib
bib <- suppressWarnings(ReadBib(here("publications_html.bib"), 
                                check = FALSE))

# Create csv of citekeys
cite_key_list <- bind_cols(
  bib$key %>% unlist %>% tibble::enframe(name = NULL), 
  bib$bibtype %>% unlist %>% tibble::enframe(name = NULL), 
  bib$year %>% unlist %>% tibble::enframe(name = NULL)
  ) %>% 
  rename(citekey = value...1, type = value...2, year = value...3) %>% 
  write_csv(here("cite_key_list.csv"))

# Set bib opions for printing
BibOptions(bib.style = "authoryear", style = "text", max.names = 10, 
           first.inits = TRUE, check.entries = FALSE)

# Convert to dataframe for analyses
dat <- bib %>% 
  as_tibble(.) %>% 
  map_df(.f = HTMLdecode) %>% 
  mutate(year = as.numeric(year))
```

And now some basic statistics on its contents:


## Citation Types

```{r, 'bibtype', fig.retina=2}
counts <- xtabs(~bibtype, data = bib) %>% as_tibble

counts %>% 
  mutate(., bibtype = fct_reorder(bibtype, n)) %>% 
  ggplot(., aes(x = bibtype, y = n, label = n)) + 
    geom_bar(stat = 'identity', color = 'black', 
             fill = 'darkred', width = 0.1) + 
    geom_point(pch = 21, size = 10, color = 'black', fill = 'lightgrey') + 
    geom_text() + 
    labs(y = "Count", x = "Citation Type") + 
    coord_flip() + 
    my_theme()
```

## Journals

```{r, 'journal', fig.retina=2}
datj <- aggregate(bibtype ~ journal, data = bib, FUN = length)

dat %>% 
  group_by(., journal) %>% 
  summarize(., counts = n(), .groups = "drop") %>% 
  na.omit() %>% 
  mutate(., journal = fct_reorder(journal, counts)) %>% 
  ggplot(., aes(x = journal, y = counts, label = counts)) + 
    geom_bar(stat = "identity", color = 'black', 
             fill = 'darkred', width = 0.1) + 
    geom_point(pch = 21, size = 10, color = 'black', fill = 'lightgrey') + 
    geom_text() + 
    labs(y = "Count", x = "Journal") + 
    coord_flip() + 
    my_theme()
```

## Authors

```{r, 'authors', fig.height=8, fig.retina=2}
# Initialize list
authors <- list()

# For each element in list, get last name of author and store in 
# 'authors' list
for (i in 1:length(bib)) {
  authors[[i]] <- bib[i]$author$family %>% unlist(.)
}

# Convert to tibble and plot
map(authors, HTMLdecode) %>% 
  unlist(.) %>% 
  enframe(.) %>% 
  group_by(., value) %>% 
  summarize(., counts = n(), .groups = "drop") %>% 
  mutate(., value = fct_reorder(value, counts)) %>% 
  ggplot(., aes(x = value, y = counts, label = counts)) + 
    geom_bar(stat = "identity", color = 'black', 
             fill = 'darkred', width = 0.1) + 
    geom_point(pch = 21, size = 10, color = 'black', fill = 'lightgrey') + 
    geom_text() + 
    labs(y = "Count", x = "Author") + 
    coord_flip() + 
    my_theme()
```

## Publication Years

```{r, 'year', fig.retina=2}
prod <- dat %>% 
  select(., year) %>% 
  na.omit(.) %>% 
  group_by(., year) %>% 
  summarize(., counts = n(), .groups = "drop") %>% 
  ungroup(.) %>% 
  mutate(., status = if_else(year <=2012, 'MA\nStudent', 
                             if_else(year <=2016, 'PhD\nStudent', 
                                     'Asst.\nProf')), 
            status = fct_relevel(status, 
                                 c('MA\nStudent', 'PhD\nStudent', 
                                   'Asst.\nProf')))

year_max <- max(prod$counts)
year_current <- prod$year %>% unique %>% max

prod %>% 
  ggplot(., aes(x = year, y = counts, label = counts)) + 
    geom_bar(stat = "identity", color = 'black', 
             fill = 'black', width = 0.1) + 
    geom_point(aes(shape = status, fill = status), size = 10, color = 'black') + 
    scale_shape_manual(name = '', values = 21:23) + 
    scale_x_continuous(breaks = seq(2009, year_current, 1)) + 
    geom_text(color = 'white') + 
    scale_fill_brewer(name = '', palette = 'Set1') + 
    labs(y = "Count", x = "Year", 
         title = "Productivity as a function of year and status") + 
    expand_limits(y = c(0, year_max + 5)) + 
    my_theme()
```

# Google scholar data

## H-index stuff

```{r, 'google-scholar'}
# Include ID
my_id <- "6sd7cVAAAAAJ"
ms_id <- "GnYMTI8AAAAJ"

miguel <- "12mgD38AAAAJ"

# Get h-index and citation history
my_h <- predict_h_index(my_id) %>% mutate(author = "jvc")
my_c <- get_citation_history(my_id) %>% mutate(author = "jvc")

# Game same info for MS
ms_h <- predict_h_index(ms_id) %>% mutate(author = "ms")
ms_c <- get_citation_history(ms_id) %>% mutate(author = "ms")

mj_h <- predict_h_index(miguel) %>% mutate(author = "miguel")
mj_c <- get_citation_history(miguel) %>% mutate(author = "miguel")

```

My current h-index is `r my_h[1, 2]`. 
I don't really know what this means (yet), but I can predict how this will grow 
over the next ten years. 

```{r, 'h-plot', fig.retina=2}
my_h %>% 
  ggplot(., aes(x = years_ahead, y = h_index)) + 
    geom_hline(yintercept = ms_h[1, 2], lty = 3) + 
    geom_path() + 
    geom_point(pch = 24, fill = "grey90", size = 3) + 
    ylim(0, max(my_h$h_index) + 5) + 
    my_theme()

ms_h %>% 
  ggplot(., aes(x = years_ahead, y = h_index)) + 
    geom_hline(yintercept = ms_h[1, 2], lty = 3) + 
    geom_path() + 
    geom_point(pch = 24, fill = "grey90", size = 3) + 
    ylim(0, max(mj_h$h_index) + 5) + 
    my_theme()
```

So it looks like I can plan on my h-index improving, but I have no context 
(yet) for what this means. 
I would like to add a few influential people to the plot to see where I 
currently fit in in relation to them. 
This might be a useful metric for setting goals. 

```{r, 'compare-h', fig.retina=2}
# Plot h-index side by side
h_index_1 <- bind_rows(my_h, ms_h, mj_h) %>% 
  ggplot(., aes(x = years_ahead, y = h_index, color = author)) + 
    geom_path() + 
    geom_point(pch = 24, fill = "grey90", size = 3) + 
    scale_color_viridis_d(option = "C", end = 0.4) + 
    labs(title = "Comparison of h-index", 
         subtitle = "Predicted h-index values over 10 years.") + 
    my_theme() + 
    theme(legend.position = c(0.15, 0.88))

# Fit a model and plot trajectories
combined_h <- bind_rows(my_h, ms_h) %>% 
  spread(author, h_index)
coefs <- lm(ms ~ jvc, data = combined_h) %>% coef

h_index_2 <- combined_h %>% 
  ggplot(., aes(x = jvc, y = ms)) + 
    geom_abline(intercept = coefs[1], slope = coefs[2], lty = 3) + 
    geom_path() + 
    geom_point(pch = 24, fill = "grey90", size = 3) + 
    my_theme()

h_index_1 + h_index_2
```

So it looks like MS has an overall higher h-index and the function shows us 
as having more or less similar growth over time. 

## Citations

Now I will take a look at my citation history. 

```{r, 'citation-history', fig.retina=2}
my_c %>% 
  ggplot(., aes(x = year, y = cites)) + 
    geom_path() + 
    geom_point(pch = 24, fill = "grey90", size = 3) + 
    my_theme()

ms_c %>% 
  ggplot(., aes(x = year, y = cites)) + 
    geom_path() + 
    geom_point(pch = 24, fill = "grey90", size = 3) + 
    ylim(0, 250) + 
    my_theme()
```

Note that these are cumulative citations by year. 

Let's plot this in comparison to MS. 

```{r 'combined-citations', fig.retina=2}
bind_rows(my_c, ms_c, mj_c) %>% 
  ggplot(., aes(x = year, y = cites, color = author)) + 
    geom_path() + 
    geom_point(pch = 24, size = 3, fill = "grey90") + 
    coord_cartesian(ylim = c(0, max(mj_c$cites) + 20)) + 
    scale_color_viridis_d(option = "C", end = 0.4) + 
    my_theme()
```

Both MS and I had bumps in year 5, but they aren't even remotely comparable. 😳

----

# Journals

## Already published or accepted

- Journal of Second Language Studies
- Second Language Research
- Phonetica
- Journal of the Acoustical Society of America
- Journal of Phonetics
- Bilingualism: Language and Cognition
- Language and Speech
- Language Learning
- Studies in SLA
- Spanish in Context
- Languages
- Translation, Cognition & Behavior

## Submitted

- Advances in Methods and Practices in Psychological Science

## In prep

- Applied Psycholinguistics (10k)
- JASA
- Language learning

## On deck

- Journal of Second Language Pronunciation
- International Journal of Bilingualism


## Wishlist

- Heritage Language Journal
- Linguistic approaches to bilingualism 
- Laboratory phonology

----

# My references (testing)

## Articles

```{r, warning=F, results='asis', echo=T}

# Printer function for refs
ref_printer <- function(pubs) {
  
  for (i in pubs) {
    print(bib[key = i]); cat("\n")
  }
  
}

```

```{r, eval=T, results='asis', echo=T}
# Filter citekey dataframe, convert to vector and use to subset bib
filter(cite_key_list, type == "Article") %>% 
  arrange(desc(year) )%>% 
  pull(citekey) %>% 
  ref_printer
```
