---
output: 
  html_document: 
    keep_md: yes
---

# mybib

Version controlled .bib file for my articles, proceedings, 
presentations, posters, and workshops.

This is a 'clean' version. It only contains UTF-8 chars (i.e. 
no ```tipa```).

This is **NOT** synchronized with my online CV (for the TODO list).

----


```{r timestamp, echo = FALSE}
message(sprintf("Last Updated: %s", Sys.time()))
```

License: Public Domain (CC-0)

I am still testing this. Initial commit is direct copy of example done by 
[@leeper](https://github.com/leeper/references). 


```{r setup, echo = FALSE, results="hide"}
library("knitr")
opts_knit$set(upload.fun = imgur_upload, base.url = NULL)
opts_chunk$set(fig.width=8, fig.height=5, cache=TRUE)
````

Here are some basic statistics on its contents:

```{r data}
library("RefManageR")
library("ggplot2")
bib <- suppressWarnings(RefManageR::ReadBib("publicationsCVclean.bib", check = FALSE))
dat <- as.data.frame(bib)
dat$year <- as.numeric(dat$year)
dat$journal[is.na(dat$journal)] <- dat$journal[is.na(dat$journal)]
```


## Citation Types

```{r bibtype}
dat$bibtype <- factor(dat$bibtype, levels = names(sort(table(dat$bibtype))))
ggplot(dat, aes(x = bibtype)) + geom_bar() + 
  xlab("Count") + ylab("Citation Type") + coord_flip()
```

## Journals

```{r journal}
datj <- aggregate(bibtype ~ journal, data = dat, FUN = length)
datj <- head(datj[order(datj$bibtype, decreasing = TRUE), ], 30)
datj$journal <- factor(datj$journal, levels = rev(datj$journal))
ggplot(datj, aes(x = journal, y = bibtype)) + geom_bar(stat = "identity") + 
  ylab("Count") + xlab("Journal") + coord_flip()
```

## Authors

```{r authors, fig.height = 8}
aut <- unlist(lapply(unlist(lapply(bib, function(x) unclass(x$author)), recursive = FALSE), `[[`, "family"))
aut <- as.data.frame(head(sort(table(aut), decreasing = TRUE), 50))
aut$aut <- factor(aut$aut, levels = rev(aut$aut))
ggplot(aut, aes(x = aut, y = Freq)) + geom_bar(stat = "identity") + 
  ylab("Count") + xlab("Author Surname") + coord_flip()
```

## Publication Years

```{r year}
ggplot(dat[dat$year > 1900, ], aes(x = year)) + geom_bar() +
  xlab("Publication Year") + ylab("Count")
```

```{r wrapup, echo = FALSE, results="hide"}
unlink("cache", recursive = TRUE)
unlink("figure", recursive = TRUE)
```
